---
title: "Demo REVTeX format to use as template"
format:
  revtex-pdf:
    keep-tex: true
    classoption:
      - aps
      - pre
      - reprint
      - superscriptaddress
author:
  - name: John Doe
    affiliations:
      - name: Dummy org
        department: Cool Dep
        address: Somewhere
        city: Magic city
        country: best one
        postal-code: 9999
      - Demo Journal
    orcid: 0000-0000-0000-0000
    email: JD@example.org
    url: https://example.org/
  - name: his friend
    affiliations:
      - Another Affiliation
abstract: |
  This document is only a demo explaining how to use the template.
keywords: [template, demo]
reference-section-title: References
bibliography: bibliography.bib
---

## Introduction {#sec-intro}

This is a dummy example only for the purpose to demonstrate the use of this repo.

This quarto extension format supports only PDF using REVTeX.

## Structure of this repository

Everything for the extensions is in `_extensions`. See Quarto doc for details. 

- In `partials`, you'll find the `.tex` partials that are used.

This repository is based on the `quarto-journals` template provided on [Github](https://github.com/quarto-journals/article-format-template).

## Demo

### Code chunk {#sec-chunks}

This format hide chunks by default as option has been set in `_extension.yml` file.

```{r}
#| prompt: true
# Loading some data but this chunk won't be shown.
data("quine", package = "MASS")
```

But you can set `echo` option to `true` locally in the chunk

```{r}
#| echo: true
m_pois <- glm(Days ~ (Eth + Sex + Age + Lrn)^2, data = quine, family = poisson)
summary(m_pois)
```

### Using references {.unnumbered}

I did not read this book [@CameronTrivedi2013] but it must be interesting.
